\LARGE \bf Planning with Attitude

### 2020-09-14 paper/main.tex
IROS submission

\section{INTRODUCTION}
    Many useful robotic systems---including quadrotors, airplanes, satellites, autonomous 
    underwater vehicles, and quadrupeds---can perform arbitrarily large three-dimensional 
    translations and rotations as part of their normal operation. 
    While representing translations is straightforward and intuitive, effectively 
    representing the nontrivial group structure of 3D rotations has been a topic of study 
    for many decades. Although we can intuitively deduce that rotations are three-dimensional, 
    a globally non-singular three-parameter representation of the space of rotations does 
    not exist \cite{stuelpnagel1964parametrization}. As a result, when parameterizing rotations, 
    we must either a) pick a three-parameter representation and deal with discontinuities, 
    or b) pick a higher-dimensional representation and deal with constraints between the 
    parameters. While simply representing attitude is nontrivial, generating and tracking 
    motion plans for floating-base systems is an even more challenging problem.

>>>>

\section{INTRODUCTION}

    Many useful robotic systems---including quadrotors, airplanes, satellites, autonomous
    underwater vehicles, and quadrupeds---can perform arbitrarily large three-dimensional
    translations and rotations as part of their normal operation. While representing
    translations is straightforward and intuitive, effectively representing the
    nontrivial group structure of 3D rotations has been a topic of study for many
    decades. Although we can intuitively deduce that rotations are three-dimensional, a
    globally non-singular three-parameter representation of the space of rotations does
    not exist \cite{stuelpnagel1964parametrization}. As a result, when parameterizing
    rotations, we must either a) pick a three-parameter representation and deal with
    discontinuities, or b) pick a higher-dimensional representation and deal with
    constraints between the parameters. While simply representing attitude is nontrivial,
    generating and tracking motion plans for floating-base systems is an even more
    challenging problem.
